\Huge ACM and Climate Change

### 2019-05-25 main.tex
Progress on a rewrite

A broad scientific consensus warns that the earth is warming due to human
emissions of carbon dioxide and other greenhouse gases (Figure
\ref{fig:warming}). This is not a problem we can leave to future
generations: we are up against it now. Indeed, the UN's Intergovernmental
Panel on Climate Change (IPCC) recently recommended a 40\% decrease in
emissions by 2030 to avoid irreversible damage
(Figure~\ref{fig:IPCC-cover}). Achieving reductions on this scale will
require urgent and sustained commitment at all levels of society, including
non-governmental communities such as universities, companies, and scientific
societies like ACM.

@@

@@

The problem of climate change is too large and too urgent to leave to world
leaders: organizations at every level must play their part by addressing
their own contributions, raising awareness among their members, and
establishing new ways of 
doing business in the lower-carbon future that is coming. For ACM, this
especially means developing strategies for reducing the climate impact of
conference-related travel.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  For example, ask the organizers of the ACM
conferences you attend what they are doing about reducing or offsetting
emissions from participants' travel.
\item {\bf Analyze} your organization's carbon-emitting activities to inform a
discussion of how best to reduce its footprint.
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\end{itemize}

\section*{More Discussions:}
\begin{itemize}
\item New comments from Judith Bishop:

>>>>

A broad scientific consensus warns that the earth is warming, due to human
emissions of carbon dioxide and other greenhouse gases (Figure
\ref{fig:warming}). This is not a problem we can leave to future
generations: we are up against it now. Indeed, the UN's Intergovernmental
Panel on Climate Change (IPCC) recently recommended a 40\% decrease in
emissions by 2030 to avoid irreversible damage
(Figure~\ref{fig:IPCC-cover}). Achieving reductions on this scale will
require urgent and sustained commitment at all levels of society, including
non-governmental communities such as universities, companies, and scientific
societies like ACM.

@@

Obviously, conferences also create value.  Science is a fundamentally social
process, and the conference system accelerates research through
opportunities for high-bandwidth interaction, direct dissemination of
results, network building, and serendipitous cross-fertilization.

This creates a dilemma: How do we weigh the environmental harm caused by
conference travel against the social benefits of the scientific progress
that comes from conferences?  This seems an extremely difficult question to
answer: the harm and the compensating benefits cannot be directly
compared---they are apples and oranges.
%
Fortunately, we have a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything: the magic of markets.  By
mapping choices to currency amounts, markets facilitate individual valuation
of costs and benefits across vastly different activities.\bcp{Give a simple,
  concrete example.} For this reason, many policy experts advocate some form
of carbon pricing, which places a monetary cost on greenhouse gas emissions,
giving a market signal that changes aggregate behavior.  Exactly what the
cost should be is a challenging question, but it has a clear ``success
criterion'': The cost should be set so that the world arrives at zero
emissions within the timeframe that climate scientists tell us is safe.

% (Experts seem to agree that the current price of around \$15 / ton is too
% low.)

Many countries and states (e.g., California) have already adopted carbon
pricing policies; more will follow.  The upshot is that, sooner or later,
carbon is going to be expensive.
\bcp{Yes, this may not happen.  But if it does not, we are probably
  screwed.  So might as well behave as if we knew it was going to happen.}
%
In the meantime, knowing that this is coming, what should we rationally (and
ethically) do now?

First, we should immediately start planning for how ACM, and computer-science
research more broadly, are going to continue to thrive in a world where air
travel is significantly more expensive.  Indeed, this may well involve
rethinking the whole basis of how computer science is done. 
\bcp{Add some meat to that.}

Second, we can begin gathering and analyzing data, to better understand both
the current carbon impact of our conferences and the likely effects (both
environmental and scientific) of potential changes in the way they are
organized.
\bcp{Put in the most interesting discussion and perhaps show an interesting
  diagram.}

\bcp{Polish and expand with reworked old text and new points.}
Finally, we can start imposing a cost on ourselves by using carbon
offsets.  (People counter-argue that this "lets people off the hook" and
encourages inaction, but we believe it is consistent with encouraging action
-- again, if offsets are priced right.)

The climate crisis is too large and too urgent to just delegate to world
leaders: organizations at every social scale must play their part by addressing
their own contributions, raising awareness among their members, and
establishing new ways of 
doing business in the lower-carbon future that is coming. For ACM, this
especially means developing strategies for reducing the climate impact of
conference-related travel.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  \bcp{Does this smack of incrementalism?
  Maybe delete it.
  ``For example, ask the organizers of the conferences you attend what they
  are doing about reducing or offsetting emissions from participants'
  travel.''}
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\item {\bf Analyze} your organization's carbon-emitting activities to inform
a discussion of how reduce its footprint and prepare for the era of
expensive carbon.
\end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities 
  \end{itemize}
}

\section*{Old Text}

@@

\section*{More Discussions:}
\begin{itemize}
\item Our notes:

Remove the IPCC image and mark the other “uninformative” image as up to the design department (i.e., we’re happy to keep it or drop it or change it to something else)

The map of registration data should be improved at least by reformatting and possibly by better data analysis, if we can get any of that done in time.  I need to schedule a meeting with Aalok and Yannick about that.

Some of the more “incremental” ideas can be removed — we included some that we ourselves were not very excited about.

We can make clearer that carbon offsets are controversial, and why

We can use the space gained by some of the above to add some discussion at the end about:

Why it’s important that ACM be serious about making serious cuts (i.e., because it gives us moral authority and sets a good example for other parts of society), even though in some sense anything that we (or any individual or “small” group does is a drop in the ocean).

The fact that ACM should also be thinking further ahead, which may mean fundamentally questioning its entire business model, along with a call to start this conversation.

\item New comments from Judith Bishop:

### 2019-05-25 rewrite.tex
Progress on a rewrite

ACM's vibrant conference culture has a dark side: it contributes
significantly to climate change. What should we do about it?

@@

Experts say that human civilization must reduce CO2 emissions by 40\%
by 2030. To do that, we all need to tighten our CO2-emitting belts. For
academic computer scientists, from what activity should the CO2 reduction come?
Look no further than our professional conferences. Air
travel is CO2 heavy, on a per-capita basis. A few trans-oceanic trips
is XXX CO2. Wow!

As responsible scientists wanting to do our part to sustain our
environment, should we eliminate (most) conferences, and thereby the
travel to organize and attend them? Doing so could impose a high cost
on scientific progress. Science is a fundamentally social process. The
conference system leverages that, accelerating research through easy
interaction, direct dissemination of results, and network building to
further new work. It works well enough that conferences are
proliferating and attendance is on the rise. So the challenge is: How
do we weigh the benefits to science of conferences against their
attendant CO2 (and other) costs? This seems like an extremely
difficult question to answer.

@@

\texdtbf{OLD STUFF HERE}

>>>>

ACM's vibrant conference culture has a dark side: it contributes
significantly to climate change. What should we do about this?

@@

Experts say that human civilization must reduce CO2 emissions by 40\% by
2030. To do that, we all need to tighten our CO2-emitting belts.  Where
should this CO2 reduction come from for computer science researchers?  Look
no further than our professional conferences. Air travel is CO2 heavy, on a
per-capita basis. A few trans-oceanic trips is XXX CO2. Wow!

As responsible scientists wanting to do our part to sustain the
habitability of the planet, should we eliminate most or all conferences, and
thus the travel to organize and attend them? Doing so could impose a high
cost on scientific progress. Science is a fundamentally social process. The
conference system leverages that, accelerating research through easy
interaction, direct dissemination of results, and network building to
further new work. It works well enough that conferences are proliferating
and attendance is on the rise. So the challenge is: How do we weigh the
benefits to science of conferences against their attendant CO2 (and other)
costs? This seems like an extremely difficult question to answer.

@@

\textbf{OLD STUFF HERE}
